### 2022-06-23 README.Rmd
update readme, namespace/desc after build

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

> Trampota F., Pajdla P., (2021). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Spatial analysis of Neolithic settlement patterns in central Europe"
```

@@

> Trampota F., Pajdla P., (2022). _`r Title`_. Journal? <https://doi.org/xxx/xxx>

The data paper accompanying this article:

> Pajdla P.. Trampota F. (2021). _Neolithic Settlements in Central Europe: Data from the Project 'Lifestyle as an Unintentional Identity in the Neolithic'_. Journal of Open Archaeology Data 9, p.13. <http://doi.org/10.5334/joad.88>.

Data is deposited in a Zenodo repository: <https://doi.org/10.5281/zenodo.5653180>.

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. Further, the analysis is divided into three 
    parts with different granularity/detail in time.
  - [:file\_folder: neo](/analysis/neo): Analysis for Neolithic B and C periods.
  - [:file\_folder: neo](/analysis/traditions): Analysis for pottery traditions.
  - [:file\_folder: neo](/analysis/groups): Analysis for pottery groups.
  - [:file\_folder: data](/analysis/data): Data used in the analysis. 
    We were not able to publish all our source data due to copyrights etc.
    There is also an individual data paper: <http://doi.org/10.5334/joad.88>.

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse, please refer to the individidual data publication at <http://doi.org/10.5334/joad.88>.
